### 2022-06-28 input/introduction.tex
meow

The rest of this paper is organized as
follows. Section~\ref{sec:background} illustrates the motivation and
problem behind our proposal.  Section~\ref{sec:adaptive} describes
dynamic consistent partitioning and its
implementation. Section~\ref{sec:experimentation} presents our
evaluations.  Section~\ref{sec:related_work} reviews related
work. Finally, Section~\ref{sec:conclusion} concludes and discusses
future work.

>>>>

The rest of this paper is organized as
follows. Sec.~\ref{sec:background} illustrates the motivation and
problem behind our proposal.  Sec.~\ref{sec:adaptive} describes
dynamic consistent partitioning and its
implementation. Sec.~\ref{sec:experimentation} presents our
evaluations.  Sec.~\ref{sec:related_work} reviews related
work. Finally, Sec.~\ref{sec:conclusion} concludes and discusses
future work.

### 2022-06-28 input/proposal.tex
meow

\begin{lemma}[\label{lem:fbfse}$\textup{FB}^+ \wedge \textup{FS}
    \centernot\implies \textup{DCP}$] Forwarding best up-to-date,
  forwarding staleness, and echoing is not sufficient to guarantee
  dynamic consistent partitioning.
\end{lemma}

@@

\begin{proof}
  %% knowing that b_p delta is sufficient to say that processes will
  %% receive delta or detect blocking
  Assuming a chain of delivery $\pi_{xz} = [x, \ldots, z]$ of
  $\alpha_x$ with $\alpha_x = \last D_z$ and $d_x(\delta_x$), we must
  prove that whatever the possible states of \nodes that belong to
  this chain, it either leads to outcome (\ref{lem:detectorA}) or
  (\ref{lem:detectorB}).
  \begin{asparadesc}
  \item [(I) Same last partition:] $\forall y \in \pi_{xz}: \alpha_x =
    \last D_y$, with forwarding of staleness
    (Definition~\ref{def:fs}), $f_{\pi_{xz}[k]}(\delta_x) \implies
    \eventually d_{\pi_{xz}[k+1]}(\delta_x)$ except if $\delta_x \in
    D_{\pi_{xz}[k+1]}$ which means that $\pi_{xz}[k+1]$ already
    delivered and forwarded $\delta_x$ following another such a chain
    of delivery. Therefore, $z$ eventually receives, hence delivers
    $\delta_x$ (outcome \ref{lem:detectorA}).

>>>>

\begin{lemma}[\label{lem:fbfse}$\textup{FB}^+ \wedge \textup{FS}
    \centernot\implies \textup{DCP}$] Forwarding best up-to-date
  and staleness, and echoing is not sufficient to guarantee
  dynamic consistent partitioning.
\end{lemma}

@@

\begin{proof}
  %% knowing that b_p delta is sufficient to say that processes will
  %% receive delta or detect blocking
  Assuming a chain of delivery $\pi_{xz} = [x, \ldots, z]$ of
  $\alpha_x$ with $\alpha_x = \last D_z$ and $d_x(\delta_x$), we must
  prove that whatever the possible states of \nodes that belong to
  this chain, it either leads to outcome (\ref{lem:detectorA}) or
  (\ref{lem:detectorB}).
  \begin{asparadesc}
  \item [(I) Same last partition:] $\forall y \in \pi_{xz}: \alpha_x =
    \last D_y$, with forwarding of staleness
    (Definition~\ref{def:fs}), $f_{\pi_{xz}[k]}(\delta_x) \implies
    \eventually d_{\pi_{xz}[k+1]}(\delta_x)$ except if $\delta_x \in
    D_{\pi_{xz}[k+1]}$ meaning that $\pi_{xz}[k+1]$ already
    delivered and forwarded $\delta_x$ following another 
    delivery chain. Therefore, $z$ eventually receives, hence delivers
    $\delta_x$ (outcome \ref{lem:detectorA}).
